Agents and you, a brief summary

### 2015-10-31 agents/summery.tex
added a markov example and how to put it in a matrix

\documentclass{article}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{bussproofs}
\usepackage{graphicx}
\usepackage{pifont}
\usepackage{qtree}
\usepackage{tikz}
\usepackage{listings}
\usepackage{hyperref}
\newenvironment{scprooftree}[1]%
{\gdef\scalefactor{#1}\begin{center}\proofSkipAmount \leavevmode}%
{\scalebox{\scalefactor}{\DisplayProof}\proofSkipAmount \end{center} }

@@

The proof is in the slides.
\subsection{Exam}
 For a given decision problem with a certain
discount factor.A pure policy sufices.
Do policy iteration, (a single iteration), do value iteration
(single iteration).

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{txfonts}
\usepackage{booktabs}
\usepackage{color}
\usepackage{bussproofs}
\usepackage{graphicx}
\usepackage{pifont}
\usepackage{qtree}
\usepackage{tikz}
\usetikzlibrary{automata,arrows,positioning,calc}
\usepackage{listings}
\usepackage{hyperref}
\newenvironment{scprooftree}[1]%
{\gdef\scalefactor{#1}\begin{center}\proofSkipAmount \leavevmode}%
{\scalebox{\scalefactor}{\DisplayProof}\proofSkipAmount \end{center} }

@@

The proof is in the slides.

\subsection{Markov to matrix}
A finite Markov process consisting of $n$ states can be represented by an 
$n\times n$ \emph{probablity transition matrix}.

Consider the following markov process:
\begin{center}
\begin{tikzpicture}[->, >=stealth', auto, semithick, node distance=3cm]
\tikzstyle{every state}=[fill=white,draw=black,thick,text=black,scale=1]
\node[state]    (A)                     {A};
\node[state]    (B)[above right of=A]   {B};
\node[state]    (C)[below right of=A]   {C};
\path
(A) edge[loop left]     node{0.5}         (A)
    edge[bend left]     node{0.3}     (B)
    edge[bend right, left]     node{0.2}      (C)
(B) edge[bend left,right]    node{0.9}      (A)
    edge[bend left,right]    node{0.1}      (C)
(C) edge[bend right, right]    node{1}      (A);
\end{tikzpicture}

The probability matrix belonging to this process looks like the following:

\[
\begin{matrix}
		& A		& B		& C \\
	A	& 0.5	& 0.3	& 0.2 \\
	B	& 0.9	& 0		& 0.1 \\
	C	& 1		& 0		& 0 \\
\end{matrix}
\]

\end{center}

Adding the $A,B,C$ is optional, but I find it gives more overview. The first
cell reads, the probobality of going from a to a.

\subsubsection{Stochastic}
A matrix where every row sums to1 is called a \emph{stochastic matrix}. Every
transition matrix is a \emph{stochastic matrix}.

\subsection{Sample path}
A \emph{sample path} of a markov chain is a specific specific realistion of
that chain.

\[ X_0,X_1,X_2,\dots\]

The $X_i$ are random variables.

\subsubsection{Markov process}
A \emph{Markov process} is a stochastic process $X_0, X_1, X_2, \dots$ such 
that:

\[ P\{ X_{n+1} X_n, X_{n-1}, \dots\}=P\{X_{n+1}|X_n\}\]
for $n \ge 0$
\subsection{Exam}
 For a given decision problem with a certain
discount factor.A pure policy sufices.
Do policy iteration, (a single iteration), do value iteration
(single iteration).
